Milestone 2: Core results 01

### 2023-01-30 R_codeP01/reports/MS2_report02.Rmd
Worked on report

```{r global-options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      echo=FALSE, warning=FALSE, message=FALSE)
```
# Data
Two clinical trails on breast cancer (advanced HR+/HER2- and HER2-E breast cancer) using two different drug combination
## Trail 1
Two treatments which differ with respect to drug combination 
- Target: ribociclib and endocrine therapy (letrozole)
- Chemotherapy: doxorubicin, cyclophosphamide and paclitaxel. 
approx. 50 patients in each group.
Endpoints: proliferation score, ROR score

## Trail 2
The primary objective of this study is to compare two cdk4/6 targeted drugs (Palbociclib, n=36; Abemaciclib, n=3 in combination with endocrine therapy (tamoxifen, fulvestrant or aromatase inhibitors,  I think?)

@@

# RESULTS

# Lasso
```{r include=TRUE}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/lb_object_AllGenes01.RData")

# Correlation
cor_vec <- as.numeric(lb_object[[1]])
sum(is.na(cor_vec))/length(cor_vec)    # fraction of NA
mean(cor_vec, na.rm=TRUE)
median(cor_vec, na.rm=TRUE)
var(cor_vec, na.rm=TRUE)
# par(mfrow=c(1,1))
hist(cor_vec, breaks = 100)

```

# Post Lasso
# Ridge
# Elastic Net
# Boosting with stumps as base learner

>>>>

# Data
One clinical trails on breast cancer (advanced HR+/HER2- and HER2-E breast cancer) using two different drug combination; and a cohorts study (here used as test data set). /
Both data set have 771 genes. This genes are specifically selected based likely potential role in breast cancer. /
The gene set is dived into X numbers of "signature genes"; which are thought to represent unities with respect to cancer biology...

## Trail
Two treatments which differ with respect to drug combination 
- Target: ribociclib and endocrine therapy (letrozole)
- Chemotherapy: doxorubicin, cyclophosphamide and paclitaxel. 
approx. 50 patients in each group.
Endpoints: proliferation score, ROR score

## Cohort
The primary objective of this study is to compare two cdk4/6 targeted drugs (Palbociclib, n=36; Abemaciclib, n=3 in combination with endocrine therapy (tamoxifen, fulvestrant or aromatase inhibitors,  I think?)

@@

# RESULTS
```{r global-options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      echo=FALSE, warning=FALSE, message=FALSE)
```

```{r}
source("/Users/anders/Documents/Master/Cancer/R_codeP01/scripts/90_output01.R")
```

# Lasso
```{r}
path <- "/Users/anders/Documents/MASTER/Cancer/model_instances/lk_AllGenesProlif.RData"
load(path)

results_lasso <- report02_out(lasso_k_ob)
```

# Ridge
# Elastic Net
# Boosting with stumps as base learner

# Post Lasso
